Peaks Over Threshold for Bursty Time Series

### 2018-04-19 article_springer/article_springer.Rmd
get packages in preamble

```{r get-rticles, eval=FALSE, include=FALSE}
# use this rticles version: 
devtools::install_github("strakaps/rticles", 
                         ref = "724aeb88d005e2f7befc37328633e7cb2bc1cce0")
# use the newest MittagLeffleR version:
devtools::install_github("strakaps/MittagLeffleR")
```

>>>>

```{r get-rticles, eval=FALSE, include=FALSE, cache=TRUE}
# use this rticles version: 
devtools::install_github("strakaps/rticles", 
                         ref = "724aeb88d005e2f7befc37328633e7cb2bc1cce0")
# use the newest MittagLeffleR version:
devtools::install_github("strakaps/MittagLeffleR")
library(MittagLeffleR)
devtools::install_github("UNSW-MATH/CTRM")
library(CTRM)
```
